Appendix: Tail associations in ecological variables and their impact on extinction risk

### 2020-04-27 SuppMat.Rmd
typo fixed

---
title: "Supporting information: Tail associations in ecological variables and their impact on extinction risk"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Daniel C. Reuman"
date: ""
fontsize: 12pt
geometry: "left=1in,right=1in,top=1in,bottom=1in"

@@

**The Ricker model.** The Ricker model was originally introduced in the context of modelling
the stock and recruitment of salmon populations, and has frequently been used in fisheries 
management. The model is 
$P(t+1)=F(P(t),r,K)=P(t) \exp[r(1-P(t)/K)]$, where $r>0$ is the intrinsic 
growth rate and $K>0$ is the carrying capacity of the population. There are two equilibrium 
states, $P_e = 0$ and $P_e = K$.
The equilibrium $P_e = 0$ is unstable, since ${F}' = \exp(r)$ for that equilibtrium, and 
$\exp(r) > 1$ for a positive $r$. Depending on $r$, 
the other equilibrium, $P_e = K$, can be stable or unstable, since ${F}' = (1-r)$. 
Specifically, $P_e=K$ is stable if $|1-r|<1$, i.e., $0<r<2$. 
The model shows undercompesatory dynamics if $0<r<1$ and overcompensatory dynamics
if $1<r<2$. Thus $r_\text{min}=0$, $r_c=1$, and $r_\text{bf}=2$.

>>>>

---
title: "Appendix: Tail associations in ecological variables and their impact on extinction risk"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Daniel C. Reuman"
date: ""
fontsize: 12pt
geometry: "left=1in,right=1in,top=1in,bottom=1in"

@@

**The Ricker model.** The Ricker model was originally introduced in the context of modelling
the stock and recruitment of salmon populations, and has frequently been used in fisheries 
management. The model is 
$P(t+1)=F(P(t),r,K)=P(t) \exp[r(1-P(t)/K)]$, where $r>0$ is the intrinsic 
growth rate and $K>0$ is the carrying capacity of the population. There are two equilibrium 
states, $P_e = 0$ and $P_e = K$.
The equilibrium $P_e = 0$ is unstable, since ${F}' = \exp(r)$ for that equilibrium, and 
$\exp(r) > 1$ for a positive $r$. Depending on $r$, 
the other equilibrium, $P_e = K$, can be stable or unstable, since ${F}' = (1-r)$. 
Specifically, $P_e=K$ is stable if $|1-r|<1$, i.e., $0<r<2$. 
The model shows undercompesatory dynamics if $0<r<1$ and overcompensatory dynamics
if $1<r<2$. Thus $r_\text{min}=0$, $r_c=1$, and $r_\text{bf}=2$.
